Operational adoption of new probabilistic point rainfall forecasts: the crucial role of a user-centric training

### 2021-01-22 manuscript/main.tex
Updates from Overleaf

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/GeoLocation_H_CR.png}}
\caption{Panel (a) shows Costa Rica location in Central America and Hungary location in Europe. Panel (b) and (c) show respectively the orography of Costa Rica and Hungary.}
\label{GeoLocation_H_CR}
\end{figure}

\section{Background on Costa Rica}
\subsection{Extreme rainfall climatology in Costa Rica}
\subsection{How does IMN traditionally forecast extreme rainfall events?}

\section{Background on Hungary}
\subsection{Extreme rainfall climatology in Hungary}
\subsection{How does OMSZ traditionally forecast extreme rainfall events?}

@@

\subsubsection{Products created for forecasters}
\begin{figure}
\centerline{\includegraphics[width=39pc]{manuscript/Figures/.jpg}}
\caption{Panel (a) shows the climate regions of Costa Rica defined by IMN. Panels from (o-1) to (o-6) show 12-hourly rainfall observations between October 3rd and 5th, 2018. Panels from (i-1) to (i-3) show the impacts caused by the extreme event in the regions in which CNE declared the state of red alert (the photos come from www.teletica.com).}
\label{Fig5}
\end{figure}

@@

@@

\subsection{Hungary}

>>>>

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/Background_GeoLocation_H_CR.png}}
\caption{Panel (a) shows Costa Rica location in Central America and Hungary location in Europe. Panel (b) and (c) show respectively the orography of Costa Rica and Hungary.}
\label{GeoLocation_H_CR}
\end{figure}

\section{Background on Costa Rica}
\subsection{Extreme rainfall climatology in Costa Rica}
\subsection{How IMN traditionally forecast extreme rainfall events}

\section{Background on Hungary}
\subsection{Extreme rainfall climatology in Hungary}
\subsection{How OMSZ traditionally forecast extreme rainfall events}

@@

\subsubsection{Development of products based on ecPoint-Rainfall}

\begin{figure}
\centerline{\includegraphics[width=19pc]{manuscript/Figures/CR_ecPoint_product.png}}
\caption{Product based on ecPoint-Rainfall created at IMN to be used by forecasters during the "real-time phase". The product consists in displaying the ecPoint-Rainfall's 85th percentile over Costa Rica.}
\label{CR_ecPoint_product}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=39pc]{manuscript/Figures/CR_ecPoint_product.png}}
\caption{Panel (a) shows the climate regions of Costa Rica defined by IMN. Panels from (o-1) to (o-6) show 12-hourly rainfall observations between October 3rd and 5th, 2018. Panels from (i-1) to (i-3) show the impacts caused by the extreme event in the regions in which CNE declared the state of red alert (the photos come from www.teletica.com).}
\label{CR_ecPoint_product}
\end{figure}

@@

\subsection{Hungary}
\subsubsection{Development of products based on ecPoint-Rainfall}
\subsubsection{Subjective Verification}
